Walling up Backdoors in Intrusion Detection Systems

### 2019-10-15 paper/paper.tex
Add ACM copyright

\def\tempYes{yes}
\documentclass[9pt,sigconf,letterpaper,dvipsnames\ifx\removeHeaders\tempYes ,nonacm\fi]{acmart}
\acmYear{2019}
\copyrightyear{2019}
\acmConference{CoNEXT '19}{December 9-12, 2019}{Orlando, Florida, USA}

>>>>

\def\tempYes{yes}
\documentclass[9pt,sigconf,letterpaper,dvipsnames\ifx\removeHeaders\tempYes ,nonacm\fi]{acmart}

\copyrightyear{2019}
\acmYear{2019}
\setcopyright{acmcopyright}
\acmConference[Big-DAMA '19]{3rd ACM CoNEXT Workshop on Big DAta, Machine Learning and Artificial Intelligence for Data Communication Networks}{December 9, 2019}{Orlando, FL, USA}
\acmBooktitle{3rd ACM CoNEXT Workshop on Big DAta, Machine Learning and Artificial Intelligence for Data Communication Networks (Big-DAMA '19), December 9, 2019, Orlando, FL, USA}
\acmPrice{15.00}
\acmDOI{10.1145/3359992.3366638}
\acmISBN{978-1-4503-6999-2/19/12}
